Migration Experience Trajectories: A Three Mode Principle Component Analysis

### 2022-05-27 preregistration/Preregistration3MPCA.Rmd
feedback added

---
title           : "Migration Experience Trajectories: A Three Mode Principle Component Analysis"
shorttitle      : "Preregistration: Migration Experience Trajectories"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1"
  - name        : Kai Epstude
    affiliation : "1"
  - name        : Rei Monden
    affiliation : "2"
  - name        : Maximilian Agostini
    affiliation : "1"
  - name        : Peter de Jonge
    affiliation : "1"
  - name        : Laura F. Bringmann
    affiliation : "1"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
  - id          : 2
    institution : Hiroshima University, Graduate School of Advanced Science and Engineering
bibliography: "../references.bib"
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
    keep_tex:  true
urlcolor: BlueViolet
citecolor: BlueViolet
linkcolor: BlueViolet
editor_options: 
  chunk_output_type: console
header-includes:
   - \usepackage{amsmath}
   - \usepackage{nccmath}
   - \usepackage{LatexPackage/trackchanges}
   # - \usepackage[finalnew]{LatexPackage/trackchanges}
   # - \usepackage[finalold]{LatexPackage/trackchanges}
   # - \usepackage[inline]{LatexPackage/trackchanges}
   - \usepackage[usenames,dvipsnames]{xcolor}
   - \addeditor{Jannis}
---

@@

@@

Given the circumstance that we utilize three independent experience sampling studies for our analyses, the variables are at times slightly different between studies. Additionally, given that the analysis we aim to undertake (i.e., 3MPCA) uses a large number of variables for the multiple imputations, dimension reduction, and correlational analyses, we will not list all items individually. Instead, we provide full variable information in the following data sheets: 'VariableSelectionDaily.xlsx' and 'VariableSelectionPrePost.xlsx'.

@@

For the detailed variable selection of each analysis see 'VariableSelectionAnalyses.xlsx'.

**Interpretation correlation variables**  
To interpret the person-mode components identified by the 3MPCA, we would like to correlate the component scores with a range of person- or time point specific variables. While the full list of variables is available in the accompanying data sheets (see 'VariableSelectionAnalyses.xlsx'), we provide a few examples of the targeted categories below.

@@

**Auxiliary variables for multiple imputation**  
For the missing data imputation we follow the procedure reported by @Monden2015, and include any pre-, post-, or daily dairy variables that are significantly ($p$ < .01) and meaningfully correlated ($r$ > .3) with either the key variables or missingness on the key variables. For an overview of the variables that qualify as auxiliary variables see the enclosed data sheets (see 'VariableSelectionAnalyses.xlsx'). Additional information about the multiple imputation procedure is also available at [Statistical models] 2.

@@

Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->
˜
1. Mean Allport's conditions. We create a mean-averaged index of Allport's conditions in response to past findings indicating that the conditions are best conceptualized jointly and as functioning together rather than as fully independent factors [@Pettigrew2006, p. 766]. Similar to past studies we thus hope to build a global indicator [e.g., see @Pettigrew2006]. As with other indices we will ensure that the individual items indeed relate to a common latent construct and are  meaningfully combined in an index. If this is not possible we will create sub-indices and/or assess the impact of the conditions separately.
    a. The interaction with [name interaction partner] was on equal footing (same status)
    a. [name interaction partner] shared your goal ([free-text entry interaction key need])
    a. The interaction with [name interaction partner] was cooperative
    a. The interaction with [name interaction partner] was voluntary
1. Mean belongingness during intergroup contact
    a. I shared information about myself. 
    a. [name interaction partner] shared information about themselves.
1. Mean alternative interaction quality definition ("Overall, the interaction with [name interaction partner] was ...")
    a. Unpleasant to Pleasant
    a. Superficial to Meaningful
    a. Ineffective to Effective
    a. Unimportant to Important
1. Mood Subscales (MDMQ)
    a. alertness
    a. calmness
    a. valence
1. Mean anti-social behaviors
    a. Put someone down
    a. Show little attention in someones opinion
    a. Demeaning remarks
    a. Inappropriately addressing someone
    a. Ignored or excluded someone
    a. Doubt someones judgement
    a. Unwanted attempts of personal matters
1. Mean pro-social behaviors
    a. Listen to someones problems
    a. Cheer someone up
    a. Help someone get things done
    a. Help someone with responsibilities

Additionally, in the pre- and post-measurement surveys are several validated scales that we will combine into their sub-scales. Indices will be created in line with their respective validation literature. For a full list of all variables and indices see 'VariableSelectionAnalyses.xlsx'.

\color{red}

\textbf{TO BE REMOVED ONCE 'VariableSelectionAnalyses.xlsx' IS DONE!}

\color{black}

\fbox{\parbox{\mylength}{
  \color{editPurple}
  \textbf{Note.}\\
  We have a group of six variables that are consistent across all three studies. Additionally, we have a number of variables that are either only relevant to a single study or a subset of the studies. If we agree on the study consolidation procedure as it is described below, I would suggest that we focus on the variables we have in all studies, and will include the other variables in the follow-up analyses and report only significant correlations (after alpha correction). I would also suggest that we add the list below to one of the variable selection files (Excel) instead of listing them all here (to avoid unnecessary confusion).
  \color{black}
}}

\color{editPurple}

Study 1 only:

1. Acculturation, Habits, and Interests Multicultural Scale for Adolescents (AHIMSA; S1)
1. Vancouver Index of Acculturation (VIA; S1)
1. Situational Self Awareness Scale (SAS; S1)

Study 3 only:

1. Outgroup Trust
1. Work Group Inclusion
1. Meaningful Life Scale
1. Big Five Personality Questionnaire
1. Attachment Styles Scale
1. Paranoia Scale

Studies 1 and 2:

1. Self Determination Theory Scale (SDT; S1, S2)
1. Interpersonal Support Evaluation List (ISEL; S1, S2)
1. Perceived Stress Scale (PSS; S1, S2)
1. Negative Life Events Scale (NLES; S1, S2)

Studies 2 and 3:

1. Social Identification Scale (S2, S3)
1. Multidimensional Mood State Questionnaire (MDMQ; S2, S3)
1. Homesickness Scale (S2, S3)

All Studies:

1. Intergroup Anxiety Scale (IAS)
1. The Satisfaction with Life Scale (SWL)
1. Rosenberg Self-Esteem Scale (SES)
1. Everyday Discrimination Scale
1. Language Proficiency
1. Association Participation

\color{black}

@@

1. **Sample Selection.** For our sample selection we address both the selection of time points and participants. Given that multiple imputation procedures even work well with large proportions of missing data [assuming missingness at random; @Madley-Dowd2019], we decided on a general criterion of less than 45% missingness to balance sample size retention and bias in the multiple imputation model. Thus, we then select the time points for which we have less than 45% missingness and select participants who have less than 45% missingness across the selected time range. Because the studies are comparable but not identical in their sampling strategy, question selection, and question wording, we also have to consider, whether to combine the samples. 
2. **Time point aggregation.** We then aggregate the key variables over time to archive a reasonably interpretable number of time points and remove a first proportion of missing data. Given that little data is available on the meaningful time scales of the selected psychological variables, we chose to determine the appropriate time scales using variance decomposition [e.g., see @Ram2014]. This is to say that we create multi-level unconditional means models (without predictors) that include possible nested time scales as levels. We chose to select time scales that align with common human cycles. We thus compare the variances of bi-daily, daily, and weekly aggregations. Additional aggregations of two weeks or the full four weeks might be possible but would most likely reduce the variance too much for any meaningul further reduction during the 3MPCA.
We then chose the ideal time scale for each of the key variables.

@@

\textbf{*Step-wise Follow-up Analyses:}
\begin{enumerate}
  \item \textbf{Three studies (S1, S2, S3)}
    \begin{enumerate}
      \item Main Analysis: Combined for most power in correlations (including, correlation with study indicator)
      \item Separate in follow up analysis to ensure that we do not have a Simpson's paradox
      \item Explore additional idiosyncratic variables in separated follow up
    \end{enumerate}
  \item \textbf{Two question types (interaction, no interaction)}:
    \begin{enumerate}
      \item Main Analysis: Combined for most power in correlations (including, correlation with interaction indicator)
      \item Separate in subgroup follow up analysis to ensure that we do not have a Simpson's paradox
    \end{enumerate}
  \item \textbf{Three time scales (half-day, day, week)}
    \begin{enumerate}
      \item Main Analysis: If all variables clearly show single most variance on the same time-scale, single analysis only
      \item If multiple time-scales are possible within single analysis, single analysis only (see question box below)
      \item If variance split across multiple time scales for substantial number of variables (> 1/4 of all variables), multiple analyses for the different time scales 
    \end{enumerate}
\end{enumerate}

>>>>

---
title           : "Migration Experience Trajectories: A Three Mode Principle Component Analysis"
shorttitle      : "Preregistration: Migration Experience Trajectories"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1"
  - name        : Kai Epstude
    affiliation : "1"
  - name        : Rei Monden
    affiliation : "2"
  - name        : Maximilian Agostini
    affiliation : "1"
  - name        : Peter de Jonge
    affiliation : "1"
  - name        : Laura F. Bringmann
    affiliation : "1"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
  - id          : 2
    institution : Hiroshima University, Graduate School of Advanced Science and Engineering
bibliography: "../references.bib"
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
    keep_tex:  true
urlcolor: BlueViolet
citecolor: BlueViolet
linkcolor: BlueViolet
editor_options: 
  chunk_output_type: console
header-includes:
   - \usepackage{amsmath}
   - \usepackage{nccmath}
   - \usepackage{enumerate}
   - \usepackage{LatexPackage/trackchanges}
   # - \usepackage[finalnew]{LatexPackage/trackchanges}
   # - \usepackage[finalold]{LatexPackage/trackchanges}
   # - \usepackage[inline]{LatexPackage/trackchanges}
   - \usepackage[usenames,dvipsnames]{xcolor}
   - \addeditor{Jannis}
---

@@

\textbf{Shortened Description:}

In this manuscript, we aim to assess the utility of a promising analysis technique for describing, summarizing, and understanding the initial developmental data patterns --- \textit{three-mode principle component analysis} (3MPCA). We use 3MPCA specifically because recent studies have laid out the potential effectiveness of dimension reduction procedures, which can address the new forms of person-, variable-, and time point heterogeneity jointly [e.g., @Monden2015]. We analyse data from three experience sampling studies, which followed the migration experiences of recent migrants to the Netherlands. All three studies focus on the psychological adaptation of migrants (i.e., psychological acculturation). However, given that past investigations of psychological acculturation have underexplored the crucial aspect of motivational experiences [@Kreienkamp2022d], the three studies have placed a particular emphasis on the needs, goals, and motives of young migrants. To make full use of all three data sets and to guide future use of dimension reduction procedures with extensive psychological data, we will analyze the data in a descriptive and step wise manner, where we first consider the data jointly and will then assess potential differences between datasets, variables, and time scales.

---

\textbf{Full Description:}

@@

Given the circumstance that we utilize three independent experience sampling studies for our analyses, the variables are at times slightly different between studies. Additionally, given that the analysis we aim to undertake (i.e., 3MPCA) uses a large number of variables for the multiple imputations, dimension reduction, and correlational analyses, we will not list all items individually. Instead, we provide full variable information in the following data sheets in `VariableSelectionAnalyses.xlsx'.

@@

For the detailed variable selection of each analysis see `VariableSelectionAnalyses.xlsx'.

**Interpretation correlation variables**  
To interpret the person-mode components identified by the 3MPCA, we would like to correlate the component scores with a range of person- or time point specific variables. While the full list of variables is available in the accompanying data sheets (see `VariableSelectionAnalyses.xlsx'), we provide a few examples of the targeted categories below.

@@

**Auxiliary variables for multiple imputation**  
For the missing data imputation we follow the procedure reported by @Monden2015, and include any pre-, post-, or daily dairy variables that are significantly ($p$ < .01) and meaningfully correlated ($r$ > .3) with either the key variables or missingness on the key variables. For an overview of the variables that qualify as auxiliary variables see the enclosed data sheets (see `VariableSelectionAnalyses.xlsx'). Additional information about the multiple imputation procedure is also available at [Statistical models] 2.

@@

Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->

1. Mean Allport's conditions. We create a mean-averaged index of Allport's conditions in response to past findings indicating that the conditions are best conceptualized jointly and as functioning together rather than as fully independent factors [@Pettigrew2006, p. 766]. Similar to past studies we thus hope to build a global indicator [e.g., see @Pettigrew2006]. As with other indices we will ensure that the individual items indeed relate to a common latent construct and are  meaningfully combined in an index. If this is not possible we will create sub-indices and/or assess the impact of the conditions separately.
    a. The interaction with [name interaction partner] was on equal footing (same status)
    a. [name interaction partner] shared your goal ([free-text entry interaction key need])
    a. The interaction with [name interaction partner] was cooperative
    a. The interaction with [name interaction partner] was voluntary
1. Mean belongingness during intergroup contact
    a. I shared information about myself. 
    a. [name interaction partner] shared information about themselves.
1. Mean alternative interaction quality definition ("Overall, the interaction with [name interaction partner] was ...")
    a. Unpleasant to Pleasant
    a. Superficial to Meaningful
    a. Ineffective to Effective
    a. Unimportant to Important
1. Mood Subscales (MDMQ)
    a. alertness
    a. calmness
    a. valence
1. Mean anti-social behaviors
    a. Put someone down
    a. Show little attention in someones opinion
    a. Demeaning remarks
    a. Inappropriately addressing someone
    a. Ignored or excluded someone
    a. Doubt someones judgement
    a. Unwanted attempts of personal matters
1. Mean pro-social behaviors
    a. Listen to someones problems
    a. Cheer someone up
    a. Help someone get things done
    a. Help someone with responsibilities

Additionally, in the pre- and post-measurement surveys are several validated scales that we will combine into their sub-scales. Indices will be created in line with their respective validation literature. For a full list of all variables and indices see `VariableSelectionAnalyses.xlsx'.

@@

1. **Sample Selection.** For our sample selection we address both the selection of time points and participants. Given that multiple imputation procedures even work well with large proportions of missing data [assuming missingness at random; @Madley-Dowd2019], we decided on a general criterion of less than 45% missingness to balance sample size retention and bias in the multiple imputation model. Thus, we then select the time points for which we have less than 45% missingness and select participants who have less than 45% missingness across the selected time range.
2. **Time point aggregation.** We aggregate the key variables over time to archive a reasonably interpretable number of time points and remove a first proportion of missing data. Given that little data is available on the meaningful time scales of the selected psychological variables, we chose to determine the appropriate time scales using variance decomposition [e.g., see @Ram2014]. This is to say that we create multi-level unconditional means models (without predictors) that include possible nested time scales as levels. We chose to select time scales that align with common human cycles. We thus compare the variances of bi-daily, daily, and weekly aggregations. Additional aggregations of two weeks or the full four weeks might be possible but would most likely reduce the variance too much for any meaningul further reduction during the 3MPCA.
We then chose the time scales that have the most variance.

@@

\textbf{*Step-wise Analysis Approach:}
\begin{enumerate}[I.]
  \item \textbf{Studies (Study 1, Study 2, Study 3)}
    \begin{itemize}
      \item \textbf{Main Analysis:} All studies combined to have the most power.
      \item \textbf{Follow-up Analysis \#01:} To make sure there is no Simpson's paradox, we also separate the three data sets in separate follow-up analyses.
      \item \textbf{Follow-up Analysis\#02:} We add idiosyncratic variables (i.e., variables only available in a subset of studies) within the separated follow-up analyses. With these additional variables we explore whether our main analysis is robust to other psychological experiences or whether the additional variables might provide a qualitatively different understanding of migration processes.
    \end{itemize}
  \item \textbf{Response types (interaction, no interaction)}\footnote{Some questions were only available or had a slightly different focus depending on whether participants had an interaction or not.}
    \begin{itemize}
      \item \textbf{Main Analysis:} All available questions combined to have the most power.
      \item \textbf{Follow-up Analysis\#03:} To make sure there is no Simpson's paradox, we separate the data into two subgroup follow-up analyses (i.e., responses following an interaction and responses without interactions). This analysis will again test the robustness of the main analysis and will explore whether the core dimensions are substantially different for interaction specific phenomena.
    \end{itemize}
  \item \textbf{Time scales (half-day, day, week)}
    \begin{itemize}
      \item \textbf{Main Analysis:} For the main analysis, we will use the time scale that shows the most variance across the included items (e.g., daily; see \textit{Time point aggregation} above).
      \item \textbf{Follow-up Analysis\#04:} To explore the impact of time scales in (social) psychological data, we will also run the 3MPCA on the other time scale options (e.g., bi-daily, weekly). 
    \end{itemize}
\end{enumerate}

### 2022-05-27 preregistration/Preregistration3MPCA.tex
feedback added

  \def\affdep{{"", "", "", "", "", ""}}%
  \def\affcity{{"", "", "", "", "", ""}}%
  \preauthor{\begin{changemargin}{-8pc}{0pc} \centering\large}
  \postauthor{\end{changemargin}}
\date{27. May 2022}
\predate{\begin{changemargin}{-8pc}{0pc} \centering\large\emph}
\postdate{\end{changemargin}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{14.0pt}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\rhead{\large\textsc{\MakeLowercase{Preregistration: Migration
Experience Trajectories}}}

\usepackage{amsmath}
\usepackage{nccmath}
\usepackage{LatexPackage/trackchanges}
\usepackage[usenames,dvipsnames]{xcolor}
\addeditor{Jannis}

@@

@@

Given the circumstance that we utilize three independent experience
sampling studies for our analyses, the variables are at times slightly
different between studies. Additionally, given that the analysis we aim
to undertake (i.e., 3MPCA) uses a large number of variables for the
multiple imputations, dimension reduction, and correlational analyses,
we will not list all items individually. Instead, we provide full
variable information in the following data sheets:
`VariableSelectionDaily.xlsx' and `VariableSelectionPrePost.xlsx'.

@@

˜ 1. Mean Allport's conditions. We create a mean-averaged index of
Allport's conditions in response to past findings indicating that the
conditions are best conceptualized jointly and as functioning together
rather than as fully independent factors \citep[p.~766]{Pettigrew2006}.
Similar to past studies we thus hope to build a global indicator
\citep[e.g., see][]{Pettigrew2006}. As with other indices we will ensure
that the individual items indeed relate to a common latent construct and
are meaningfully combined in an index. If this is not possible we will
create sub-indices and/or assess the impact of the conditions
separately. a. The interaction with {[}name interaction partner{]} was
on equal footing (same status) a. {[}name interaction partner{]} shared
your goal ({[}free-text entry interaction key need{]}) a. The
interaction with {[}name interaction partner{]} was cooperative a. The
interaction with {[}name interaction partner{]} was voluntary 1. Mean
belongingness during intergroup contact a. I shared information about
myself. a. {[}name interaction partner{]} shared information about
themselves. 1. Mean alternative interaction quality definition
(``Overall, the interaction with {[}name interaction partner{]} was
\ldots{}'') a. Unpleasant to Pleasant a. Superficial to Meaningful a.
Ineffective to Effective a. Unimportant to Important 1. Mood Subscales
(MDMQ) a. alertness a. calmness a. valence 1. Mean anti-social behaviors
a. Put someone down a. Show little attention in someones opinion a.
Demeaning remarks a. Inappropriately addressing someone a. Ignored or
excluded someone a. Doubt someones judgement a. Unwanted attempts of
personal matters 1. Mean pro-social behaviors a. Listen to someones
problems a. Cheer someone up a. Help someone get things done a. Help
someone with responsibilities

@@

\color{red}

\textbf{TO BE REMOVED ONCE 'VariableSelectionAnalyses.xlsx' IS DONE!}

\color{black}

\fbox{\parbox{\mylength}{
  \color{editPurple}
  \textbf{Note.}\\
  We have a group of six variables that are consistent across all three studies. Additionally, we have a number of variables that are either only relevant to a single study or a subset of the studies. If we agree on the study consolidation procedure as it is described below, I would suggest that we focus on the variables we have in all studies, and will include the other variables in the follow-up analyses and report only significant correlations (after alpha correction). I would also suggest that we add the list below to one of the variable selection files (Excel) instead of listing them all here (to avoid unnecessary confusion).
  \color{black}
}}

\color{editPurple}

Study 1 only:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Acculturation, Habits, and Interests Multicultural Scale for
  Adolescents (AHIMSA; S1)
\item
  Vancouver Index of Acculturation (VIA; S1)
\item
  Situational Self Awareness Scale (SAS; S1)
\end{enumerate}

Study 3 only:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Outgroup Trust
\item
  Work Group Inclusion
\item
  Meaningful Life Scale
\item
  Big Five Personality Questionnaire
\item
  Attachment Styles Scale
\item
  Paranoia Scale
\end{enumerate}

Studies 1 and 2:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Self Determination Theory Scale (SDT; S1, S2)
\item
  Interpersonal Support Evaluation List (ISEL; S1, S2)
\item
  Perceived Stress Scale (PSS; S1, S2)
\item
  Negative Life Events Scale (NLES; S1, S2)
\end{enumerate}

Studies 2 and 3:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Social Identification Scale (S2, S3)
\item
  Multidimensional Mood State Questionnaire (MDMQ; S2, S3)
\item
  Homesickness Scale (S2, S3)
\end{enumerate}

All Studies:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Intergroup Anxiety Scale (IAS)
\item
  The Satisfaction with Life Scale (SWL)
\item
  Rosenberg Self-Esteem Scale (SES)
\item
  Everyday Discrimination Scale
\item
  Language Proficiency
\item
  Association Participation
\end{enumerate}

\color{black}

@@

  missingness across the selected time range. Because the studies are
  comparable but not identical in their sampling strategy, question
  selection, and question wording, we also have to consider, whether to
  combine the samples.

@@

  \textbf{Time point aggregation.} We then aggregate the key variables
  over time to archive a reasonably interpretable number of time points
  and remove a first proportion of missing data. Given that little data
  is available on the meaningful time scales of the selected
  psychological variables, we chose to determine the appropriate time
  scales using variance decomposition \citep[e.g., see][]{Ram2014}. This
  is to say that we create multi-level unconditional means models
  (without predictors) that include possible nested time scales as
  levels. We chose to select time scales that align with common human
  cycles. We thus compare the variances of bi-daily, daily, and weekly

@@

  chose the ideal time scale for each of the key variables.

@@

\textbf{*Step-wise Follow-up Analyses:}

\begin{enumerate}
  \item \textbf{Three studies (S1, S2, S3)}
    \begin{enumerate}
      \item Main Analysis: Combined for most power in correlations (including, correlation with study indicator)
      \item Separate in follow up analysis to ensure that we do not have a Simpson's paradox
      \item Explore additional idiosyncratic variables in separated follow up
    \end{enumerate}
  \item \textbf{Two question types (interaction, no interaction)}:
    \begin{enumerate}
      \item Main Analysis: Combined for most power in correlations (including, correlation with interaction indicator)
      \item Separate in subgroup follow up analysis to ensure that we do not have a Simpson's paradox
    \end{enumerate}
  \item \textbf{Three time scales (half-day, day, week)}
    \begin{enumerate}
      \item Main Analysis: If all variables clearly show single most variance on the same time-scale, single analysis only
      \item If multiple time-scales are possible within single analysis, single analysis only (see question box below)
      \item If variance split across multiple time scales for substantial number of variables (> 1/4 of all variables), multiple analyses for the different time scales 
    \end{enumerate}
\end{enumerate}

>>>>

  \def\affdep{{"", "", "", "", "", ""}}%
  \def\affcity{{"", "", "", "", "", ""}}%
  \preauthor{\begin{changemargin}{-8pc}{0pc} \centering\large}
  \postauthor{\end{changemargin}}
\date{28. May 2022}
\predate{\begin{changemargin}{-8pc}{0pc} \centering\large\emph}
\postdate{\end{changemargin}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{14.0pt}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\rhead{\large\textsc{\MakeLowercase{Preregistration: Migration
Experience Trajectories}}}

\usepackage{amsmath}
\usepackage{nccmath}
\usepackage{enumerate}
\usepackage{LatexPackage/trackchanges}
\usepackage[usenames,dvipsnames]{xcolor}
\addeditor{Jannis}

@@

\textbf{Shortened Description:}

In this manuscript, we aim to assess the utility of a promising analysis
technique for describing, summarizing, and understanding the initial
developmental data patterns ---
\textit{three-mode principle component analysis} (3MPCA). We use 3MPCA
specifically because recent studies have laid out the potential
effectiveness of dimension reduction procedures, which can address the
new forms of person-, variable-, and time point heterogeneity jointly
\citep[e.g.,][]{Monden2015}. We analyse data from three experience
sampling studies, which followed the migration experiences of recent
migrants to the Netherlands. All three studies focus on the
psychological adaptation of migrants (i.e., psychological
acculturation). However, given that past investigations of psychological
acculturation have underexplored the crucial aspect of motivational
experiences \citep{Kreienkamp2022d}, the three studies have placed a
particular emphasis on the needs, goals, and motives of young migrants.
To make full use of all three data sets and to guide future use of
dimension reduction procedures with extensive psychological data, we
will analyze the data in a descriptive and step wise manner, where we
first consider the data jointly and will then assess potential
differences between datasets, variables, and time scales.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{Full Description:}

@@

Given the circumstance that we utilize three independent experience
sampling studies for our analyses, the variables are at times slightly
different between studies. Additionally, given that the analysis we aim
to undertake (i.e., 3MPCA) uses a large number of variables for the
multiple imputations, dimension reduction, and correlational analyses,
we will not list all items individually. Instead, we provide full
variable information in the following data sheets in
`VariableSelectionAnalyses.xlsx'.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Mean Allport's conditions. We create a mean-averaged index of
  Allport's conditions in response to past findings indicating that the
  conditions are best conceptualized jointly and as functioning together
  rather than as fully independent factors
  \citep[p.~766]{Pettigrew2006}. Similar to past studies we thus hope to
  build a global indicator \citep[e.g., see][]{Pettigrew2006}. As with
  other indices we will ensure that the individual items indeed relate
  to a common latent construct and are meaningfully combined in an
  index. If this is not possible we will create sub-indices and/or
  assess the impact of the conditions separately.

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    The interaction with {[}name interaction partner{]} was on equal
    footing (same status)
  \item
    {[}name interaction partner{]} shared your goal ({[}free-text entry
    interaction key need{]})
  \item
    The interaction with {[}name interaction partner{]} was cooperative
  \item
    The interaction with {[}name interaction partner{]} was voluntary
  \end{enumerate}
\item
  Mean belongingness during intergroup contact

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    I shared information about myself.
  \item
    {[}name interaction partner{]} shared information about themselves.
  \end{enumerate}
\item
  Mean alternative interaction quality definition (``Overall, the
  interaction with {[}name interaction partner{]} was \ldots{}'')

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    Unpleasant to Pleasant
  \item
    Superficial to Meaningful
  \item
    Ineffective to Effective
  \item
    Unimportant to Important
  \end{enumerate}
\item
  Mood Subscales (MDMQ)

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    alertness
  \item
    calmness
  \item
    valence
  \end{enumerate}
\item
  Mean anti-social behaviors

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    Put someone down
  \item
    Show little attention in someones opinion
  \item
    Demeaning remarks
  \item
    Inappropriately addressing someone
  \item
    Ignored or excluded someone
  \item
    Doubt someones judgement
  \item
    Unwanted attempts of personal matters
  \end{enumerate}
\item
  Mean pro-social behaviors

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    Listen to someones problems
  \item
    Cheer someone up
  \item
    Help someone get things done
  \item
    Help someone with responsibilities
  \end{enumerate}
\end{enumerate}

@@

@@

  missingness across the selected time range.

@@

  \textbf{Time point aggregation.} We aggregate the key variables over
  time to archive a reasonably interpretable number of time points and
  remove a first proportion of missing data. Given that little data is
  available on the meaningful time scales of the selected psychological
  variables, we chose to determine the appropriate time scales using
  variance decomposition \citep[e.g., see][]{Ram2014}. This is to say
  that we create multi-level unconditional means models (without
  predictors) that include possible nested time scales as levels. We
  chose to select time scales that align with common human cycles. We
  thus compare the variances of bi-daily, daily, and weekly

@@

  chose the time scales that have the most variance.

@@

\textbf{*Step-wise Analysis Approach:}

\begin{enumerate}[I.]
  \item \textbf{Studies (Study 1, Study 2, Study 3)}
    \begin{itemize}
      \item \textbf{Main Analysis:} All studies combined to have the most power.
      \item \textbf{Follow-up Analysis \#01:} To make sure there is no Simpson's paradox, we also separate the three data sets in separate follow-up analyses.
      \item \textbf{Follow-up Analysis\#02:} We add idiosyncratic variables (i.e., variables only available in a subset of studies) within the separated follow-up analyses. With these additional variables we explore whether our main analysis is robust to other psychological experiences or whether the additional variables might provide a qualitatively different understanding of migration processes.
    \end{itemize}
  \item \textbf{Response types (interaction, no interaction)}\footnote{Some questions were only available or had a slightly different focus depending on whether participants had an interaction or not.}
    \begin{itemize}
      \item \textbf{Main Analysis:} All available questions combined to have the most power.
      \item \textbf{Follow-up Analysis\#03:} To make sure there is no Simpson's paradox, we separate the data into two subgroup follow-up analyses (i.e., responses following an interaction and responses without interactions). This analysis will again test the robustness of the main analysis and will explore whether the core dimensions are substantially different for interaction specific phenomena.
    \end{itemize}
  \item \textbf{Time scales (half-day, day, week)}
    \begin{itemize}
      \item \textbf{Main Analysis:} For the main analysis, we will use the time scale that shows the most variance across the included items (e.g., daily; see \textit{Time point aggregation} above).
      \item \textbf{Follow-up Analysis\#04:} To explore the impact of time scales in (social) psychological data, we will also run the 3MPCA on the other time scale options (e.g., bi-daily, weekly). 
    \end{itemize}
\end{enumerate}
